### 2024-08-01 paper/Cover_letter_Indecisions.tex
submitted
updated cover letter

We are writing to request that you consider our paper, \textcolor{myudblue}{\textbf{``Indecision under time pressure arises from suboptimal switching behaviour''}}, for publication in \emph{Current Biology}.

@@

Tony Carlsen, University of Ottawa, University of Ottawa

@@

%Tony Carlsen, University of Ottawa, University of Ottawa

>>>>

We are writing to request that you consider our paper, \textcolor{myudblue}{\textbf{``Indecision under time pressure arises from suboptimal switching behaviour''}}, for publication in \emph{Proceedings of the National Academy of Sciences}.
\vspace{3.0mm}

@@

Tony Carlsen, University of Ottawa, acarlsen@uottawa.ca

@@
